Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-28 publication/manuscript.Rmd
switch citation style

#date: "`r Sys.Date()`"
bibliography: literature.bib
#linenumbers: true
numbersections: true
output:
  #rticles::elsevier_article: default
  bookdown::pdf_book:
    base_format: rticles::springer_article
bibstyle: spphys

>>>>

#date: "`r Sys.Date()`"
bibliography: literature.bib
#linenumbers: true
numbersections: true
output:
  #rticles::elsevier_article: default
  bookdown::pdf_book:
    base_format: rticles::springer_article
#bibstyle: spphys
csl: elsevier-harvard.csl
